Numerical Solution of Point Defect Equations by MOOSE

### 2021-01-08 examples/point_defects/article/article.tex
article-edit

\documentclass[a4paper]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{verbatim}
\pagenumbering{arabic}
\graphicspath{ {./plots/} }

@@

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
      \caption{Average Concentration profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
      \label{figure:average_concentrations_neutron_5}
    \end{figure}

@@

    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
      \caption{Concentration profiles for low dose rate neutron irradation with 0\% Production Bias}
      \label{figure:concentrations_neutron_0_1e-6}
    \end{figure}
    \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
      \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
      \label{figure:concentrations_neutron_0_1e-3}
    \end{figure}
    \newpage
     If production bias (\%5) is applied, the steady state concentration profiles change considerably. The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig. \ref{figure:concentrations_neutron_5_1e-6}a). Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary. The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig. \ref{figure:concentrations_neutron_5_1e-6}b.\\
    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
      \caption{Concentration profiles for low dose rate neutron irradation with 5\% Production Bias}
      \label{figure:concentrations_neutron_5_1e-6}
    \end{figure}\\

    Similar to unbiased case, average concentration levels increases with dose rate. But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig. \ref{figure:concentrations_neutron_5_1e-3}).\\
    \begin{figure}[htb!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
      \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
      \label{figure:concentrations_neutron_5_1e-3}
    \end{figure}

@@

    The vacancy supersaturation curves for biased neutron irradation is given in Fig. \ref{figure:vacancy_supersaturation_neutron_5}. Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center. The plot shows a non-linear increase in supersaturation values as grain gets larger.
      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_neutron_5}
      \end{figure}

@@

  The results of bencmark problem, previously discussed in Fig. \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations. Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
    \begin{table}[h!]
      \centering
      \caption{Comparison of sink strength calculations}
      \label{table:sink_strengths_calculations}
      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
         \hline
          & MOOSE & Analytical\\
         \hline\hline\hline
         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         \hline
      \end{tabular}
    \end{table}
    \newpage
    Sink strength plots are presented in Fig. \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}. The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm. In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig. \ref{figure:sink_strengths_neutron_5_1e-6}b).
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
        \caption{GB Sink Strength for low(a) and high(b) dose neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}

      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
        \caption{Total GB Sink Strengths for high dose neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-3}
      \end{figure}

      \newpage
      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
        \qquad
        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
        \caption{Sink Strengths for low dose rate neutron irradiation}
        \label{figure:sink_strength_moose_neutron_3D}
      \end{figure}

      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron}}
        \qquad
        % \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
        \caption{GB Sink Strengths for low dose rate neutron irradation}
        \label{figure:sink_strengths_neutron_bias_Z}
      \end{figure}

      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron}}
        \qquad
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
        \caption{Total GB Sink Strengths for low dose rate neutron irradation}
        \label{figure:sink_strengths_neutron_bias_k}
      \end{figure}

  \newpage
  \subsection{Ion Irradiation} \hspace{10pt}
  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic. Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions. These characteristic causes a non-uniform defect production profile. Figure \ref{figure:defect_production} shows the profile used for ion irradation simulations. The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but the profile doesn't change.
    \begin{figure}[h!]  %Ion irradation
      \centering
      \subfloat{\includegraphics[scale=0.27]{defect_production}}
      \qquad
      \caption{Defect production profile for ion irradation.}
      \label{figure:defect_production}
    \end{figure}
    \subsubsection{Concentrations} \hspace{10pt}
    Even though ion irradation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradation case. The only difference is the change in concentration levels as a result of less defect production (see Fig. \ref{figure:average_concentrations_ion_5}).

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
      \caption{Average Concentration profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
      \label{figure:average_concentrations_ion_5}
    \end{figure}

    \newpage
    The effect of defect production distribution can be observed obviously in concentration profiles. Since, defect production has peak at around half of the grain, the concentration profiles are taking shape under same behavior and reaching maximum at the center of domain, then waning through boundaries.

    If production bias is zero, maximum concentration of each type of point defect becomes independent of grain sizes shown in Fig. \ref{figure:concentrations_ion_0_1e-6}. High ion dose rate only scales up the concentration levels without making any significant change in profiles (see Fig. \ref{figure:concentrations_ion_0_1e-3}).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for high dose rate ion irradiation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-3}
      \end{figure}
      \newpage
      In case of applying production bias, profiles become completely different. The flipping behavior observed in neutron irradation case repeats on ion irradation case. In addition, the non-uniform defect production causes asymmetrical interstitial concentration profile given in Fig. \ref{figure:concentrations_ion_5_1e-6}a. The vacancy concentration profiles also loose their symmetry and shift up with increasing grain size (see Fig. \ref{figure:concentrations_ion_5_1e-6}b). Increase on ion dose rate, from 1e-6 dpa/s to 1e-3 dpa/s, combines with the effect of defect production profile and reduces the critical grain size to ${\sim}$250 nm. The flipping start to be visible through end of the grains. (see Fig. \ref{figure:concentrations_ion_5_1e-3}a).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for high dose rate ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-3}
      \end{figure}

@@

    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case. The only difference is the asymmetrical shape of curves originates from concentration profiles. The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
      \begin{figure}[h!]  %Ion - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
        \caption{Vacancy Supersaturation profiles for low(a) and high(b) dose ion irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_ion_5}
      \end{figure}
      \newpage
    \subsubsection{Sink Strengths} \hspace{10pt}
    The sink strengths are directly related to concentration at center and flow at boundary. The change in centerline defect concentrations are not as considerable as neutron case. So, the flow or flux at boundary becomes more dominant on sink strength profiles (see Fig. \ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
      %   \centering
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
      %   \qquad
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
      %   \label{figure:sink_strengths_ion_0_1e-6}
      % \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
        \qquad
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
        \caption{GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
        \label{figure:sink_strengths_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
        \caption{Total GB Sink Strengths for low(a) and high(b) dose rate ion irradiation with 5\% Production Bias}
        \label{figure:sink_strengths_ion_5_1e-3}
      \end{figure}

>>>>

\documentclass[a4paper]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[font=scriptsize]{caption}
\pagenumbering{arabic}
\graphicspath{ {./plots/} }

@@

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
      \label{figure:average_concentrations_neutron_5}
    \end{figure}

@@

    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
      \caption{Concentration profiles for low neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-6}
    \end{figure}
    \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-3}
    \end{figure}
    \newpage
     If production bias (\%5) is applied, the steady state concentration profiles change considerably. The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig. \ref{figure:concentrations_neutron_5_1e-6}a). Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary. The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig. \ref{figure:concentrations_neutron_5_1e-6}b.\\
    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
      \caption{Concentration profiles for low neutron dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_5_1e-6}
    \end{figure}\\

    Similar to unbiased case, average concentration levels increases with dose rate. But, the most important effect of high neutron dose rate is causing the interstitial concentration profile to flip in smaller grain sizes than 500 nm (see Fig. \ref{figure:concentrations_neutron_5_1e-3}).\\
    \begin{figure}[htb!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}}
      \caption{Concentration profiles for high neutron dose rate with 0\% production bias, a) interstitial concentration b) vacancy concentration}
      \label{figure:concentrations_neutron_5_1e-3}
    \end{figure}

@@

    The vacancy supersaturation curves for biased neutron irradation is given in Fig. \ref{figure:vacancy_supersaturation_neutron_5}. Since the defect concentrations have symmetrical profiles for neutron irradation, supersaturation curves are also symmetrical around grain center. The plot shows a non-linear increase in supersaturation values as grain gets larger.
      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy supersaturation profiles for 5\% production bias, a)low neutron dose rate, b) high neutron dose rate}
        \label{figure:vacancy_supersaturation_neutron_5}
      \end{figure}

@@

  The results of bencmark problem, previously discussed in Fig. \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations. Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
    \begin{table}[h!]
      \centering
      \caption{Comparison of sink strength calculations}
      \label{table:sink_strengths_calculations}
      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
         \hline
          & MOOSE & Analytical\\
         \hline\hline\hline
         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         \hline
      \end{tabular}
    \end{table}
    \newpage
    Sink strength plots are presented in Fig. \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}. The effect of flipping behavior is not visible in the plot of grain boundary sink strength, ${Z^{gb}}$, but there is a significant change on total grain boundary sink strength, ${k^2_i}$ after critical grain size of ${\sim}$1000 nm. In case of high dose rate, the critical grain size drops to ${\sim}$250 nm (Fig. \ref{figure:sink_strengths_neutron_5_1e-6}b).
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}

      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
        \label{figure:sink_strengths_neutron_5_1e-3}
      \end{figure}

      \newpage
      The calculated sink strengths for different production bias and for different grain sizes are presented by a 3D surface plot as given in Fig. \ref{figure:sink_strength_moose_neutron_3D}.
      \begin{figure}[h!]  %Sink Strength 3D - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Zi_scaled}}
        \subfloat{b)\includegraphics[scale=0.5]{sink_strength_moose_neutron_3D_Zv_scaled}}
        \qquad
        \subfloat{c)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_ki_scaled}}
        \subfloat{d)\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_kv_scaled}}
        \caption{Change of sink strengths with grain size and production bias for low neutron dose rate in log scale, a)interstitial GB sink strength, b) vacancy GB sink strength, c) total interstitial GB sink strength, d) total vacancy GB sink strength}
        \label{figure:sink_strength_moose_neutron_3D}
      \end{figure}

      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_Zi_scaled_nolegend}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_Zv_scaled_nolegend}}
        \subfloat{\includegraphics[scale=0.35]{legend}}
        \qquad
        % \subfloat{a)\includegraphics[scale=0.55]{sink_strength_Zi_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_Zv_scaled_neutron_500-5000nm}}
        \caption{Change of sink strengths with production bias for low neutron dose rate, a) interstitial GB sink strength, b) vacancy GB sink strength}
        \label{figure:sink_strengths_neutron_bias_Z}
      \end{figure}

      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_neutron_ki_scaled_nolegend}}
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_neutron_kv_scaled_nolegend}}                \subfloat{\includegraphics[scale=0.35]{legend}}
        \qquad
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_ki_scaled_neutron_500-5000nm}}
        % \subfloat{b)\includegraphics[scale=0.55]{sink_strength_kv_scaled_neutron_500-5000nm}}
        \caption{Change of sink strengths with production bias for low neutron dose rate, a) total interstitial GB sink strength, b) total vacancy GB sink strength}
        \label{figure:sink_strengths_neutron_bias_k}
      \end{figure}

  \newpage
  \subsection{Ion Irradiation} \hspace{10pt}
  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic. Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions. These characteristic causes a non-uniform defect production profile. Figure \ref{figure:defect_production} shows the profile used for ion irradation simulations. The dose rate, K\textsubscript{0} and grain size (1000 nm) would be scaled for the case of interest, but the profile doesn't change.
    \begin{figure}[h!]  %Ion irradation
      \centering
      \subfloat{\includegraphics[scale=0.27]{defect_production}}
      \qquad
      \caption{Defect production profile for ion irradation.}
      \label{figure:defect_production}
    \end{figure}
    \newpage
    \subsubsection{Concentrations} \hspace{10pt}
    Even though ion irradation has non-uniform defect production, average defect concentrations show a time-dependent trend that is identical to the one in neutron irradation case. The only difference is the change in concentration levels as a result of less defect production (see Fig. \ref{figure:average_concentrations_ion_5}).

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a) low ion dose rate, b) high ion dose rate}
      \label{figure:average_concentrations_ion_5}
    \end{figure}

    The effect of defect production distribution can be observed obviously in concentration profiles. Since, defect production has peak at around half of the grain, the concentration profiles are taking shape under same behavior and reaching maximum at the center of domain, then waning through boundaries.

    If production bias is zero, maximum concentration of each type of point defect becomes independent of grain sizes shown in Fig. \ref{figure:concentrations_ion_0_1e-6}. High ion dose rate only scales up the concentration levels without making any significant change in profiles (see Fig. \ref{figure:concentrations_ion_0_1e-3}).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for low ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
        \label{figure:concentrations_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for high ion dose rate with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
        \label{figure:concentrations_ion_0_1e-3}
      \end{figure}
      \newpage
      In case of applying production bias, profiles become completely different. The flipping behavior observed in neutron irradation case repeats on ion irradation case. In addition, the non-uniform defect production causes asymmetrical interstitial concentration profile given in Fig. \ref{figure:concentrations_ion_5_1e-6}a. The vacancy concentration profiles also loose their symmetry and shift up with increasing grain size (see Fig. \ref{figure:concentrations_ion_5_1e-6}b). Increase on ion dose rate, from 1e-6 dpa/s to 1e-3 dpa/s, combines with the effect of defect production profile and reduces the critical grain size to ${\sim}$250 nm. The flipping start to be visible through end of the grains. (see Fig. \ref{figure:concentrations_ion_5_1e-3}a).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for low ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
        \label{figure:concentrations_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for high ion dose rate with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
        \label{figure:concentrations_ion_5_1e-3}
      \end{figure}

@@

    The vacancy supersaturation curves for ion irradation case are quite similar to ones for neutron irradation case. The only difference is the asymmetrical shape of curves originates from concentration profiles. The non-linear increase in supersaturation values as domain gets larger is observed for ion irradation too.
      \begin{figure}[h!]  %Ion - %5 Bias rate
        \centering
        \subfloat{a)\includegraphics[scale=0.55]{super_saturation_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{super_saturation_500-5000nm-ion-5}}
        \caption{Vacancy supersaturation profiles for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
        \label{figure:vacancy_supersaturation_ion_5}
      \end{figure}
      \newpage
    \subsubsection{Sink Strengths} \hspace{10pt}
    The sink strengths are directly related to concentration at center and flow at boundary. The change in centerline defect concentrations are not as considerable as neutron case. So, the flow or flux at boundary becomes more dominant on sink strength profiles (see Fig. \ref{figure:sink_strengths_ion_5_1e-6} and \ref{figure:sink_strengths_ion_5_1e-3}).
      % \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
      %   \centering
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_k}}
      %   \qquad
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_ion_0_Z}}
      %   \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
      %   \label{figure:sink_strengths_ion_0_1e-6}
      % \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_Z_scaled}}
        \qquad
        \subfloat{a)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_Z_scaled}}
        \caption{Change of GB sink strength with grain size for 5\% production bias, a) low ion dose rate, b) high ion dose rate}
        \label{figure:sink_strengths_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_low_ion_5_k_scaled}}
        \qquad
        \subfloat{b)\includegraphics[scale=0.55]{sink_strength_moose_ion_5_k_scaled}}
        \caption{Change of total GB sink strength with grain size for 5\% production bias, a) low neutron dose rate, b) high neutron dose rate}
        \label{figure:sink_strengths_ion_5_1e-3}
      \end{figure}
